Does personal relevance attenuate citizens' persuasion by government branding? Evidence from a survey experiment on air-pollution policy

### 2019-07-22 paper3_revision_text.Rmd
Add files via upload

Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order). They were informed that these plans were obtained from EPM's annual work plan. The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols". In the real symbols condition, the two policies are displayed with three symbolic elements, which have been used in EPM's public communications, and became widely recognized by the public. The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second element is the green color, which is strongly associated with taking care of the environment. The third element is an image of a celebrity comedian from an advertising campaign of the EPM. The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman. The recycling policy (in the real symbols condition) was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images. Finally, in the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people. The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic brand elements (i.e. the symbolic effect) from a possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy. The symbols conditions are displayed in **Appendix B**. Further details about the real and fake symbols are found in section ## of the supplementary appendix.

@@

Each policy plan was followed by six questions about respondents' trust in the policy. After the trust questions of the second policy, the subjects were asked additional questions about the two policies, including the degree to which they perceive each of them as personally relevant. These questions were followed by an Instructional Manipulation Check (IMC) item, intended to assess participants’ diligence. The last sections included a set of demographic questions including questions about their place of residence and work, and manipulation checks for participants' familiarity with the real symbols. At the end of the survey, the participants were debriefed about the manipulations, and the possible deception.

In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy. I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions. Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations. I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the relevant two-way interactions. I conducted these estimations after the data collection and analyses, based on the analytical sample size. The estimated detectable interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs. As for the interactions with the relevance manipulation (among Haifa Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively. The power estimations are reported in details in Section ## of the supplementary appendix.

@@

[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings. ##add check reliability of information. ##

@@

`r table.x=table.x+1`**Tables `r table.x`** compares between the different experimental conditions, within each of the two areas, on demographic variables and pre-manipulation covariates. These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues. Yet, Haifa Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.

[^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups -- regarding education levels and the percentage of parents; and between the information groups -- regarding the percentage of parents for young children. To adjust for small finite-sample imbalances, as well as for differences between the areas, I control for covariates.

@@

I now turn to exploring respondents trust in the *air-pollution policy*. This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy. `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas. The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`]. Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test). The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score. Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a very low score of 2 or less, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group. As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`]. Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than the middle point 4 (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects). This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.

@@

Next, I examine the interactions between the symbols and information manipulation, and the two areas. To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>). Likewise, I expect Haifa Bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H<sub>2</sub>). `r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa Bay area. Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group. The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups. However, these differences were smaller compared with the effect among the Haifa Bay subjects, and not sufficiently significant. The effects of the information manipulation on the two groups are presented in the right panel. This comparison shows that the differences between participants' trust in the weak and strong policies were roughly similar in both groups.

[^footnote_raw_means]: In addition, raw means and SDs of outcome variables across the two areas are reported in section XX of the supplementary appendix.

@@

These results are at odds with the two theoretical hypotheses. They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition. Additionally, these analyses do not provide evidence that the more engaged Haifa Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.

@@

[^footnote_heteroskedacity]: Breusch-Pagan test confirms that the null hypotheses that the variance of the residuals is constant. For Model 1.3, Breusch-Pagan test =  `r bptest(mod_air_1.3)[["statistic"]][["BP"]] %>% round(3)`, *p*=`r bptest(mod_air_1.3)[["p.value"]][["BP"]] %>% round(3)`. Robust standard errors are estimated using R sandwich package with estimation type "HC1".

@@

Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content. Accordingly, they do not support the research hypotheses. Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence I cannot rule out a concern of endogeneity. Accordingly, the null findings regarding the interactions between the areas and the manipulations can be a result by other, unobserved differences between the two populations. As explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation. I now discuss the results of these two tests.

`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`). Overall, these models reveal relatively similar patterns to those found in the air-pollution policy. Notice that Haifa Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry. The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information. The fact that similar patterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance. It also rules out a possible argument that greater relevance enhances (rather then reduces) the effect of symbols. If this was the case, then there should have been no interaction between symbols and the areas for the recycling policy.

@@

Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations. In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations. Similarly to the regression tables presented above, the final two models are robust analyses where I add controls (Model `r table.x`.3) and restrict the sample to the policy presented first in order (Model `r table.x`.4). In all these models, the coefficient of the relevance treatment is negative but far from significance. The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the averaged differences between those who saw the symbols and those who did not were slightly smaller. However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group) and far from significance. The interactions between the relevance treatment and weak information manipulations are positive but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]

@@

How can we reconcile the findings of this study with the proposed theory? One plausible explanation is that despite the relatively high involvement of Haifa Bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues. If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance. Indeed, Petty and Cacioppo have admitted that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p. 206].

>>>>

Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order). They were informed that these plans were obtained from EPM's annual work plan. The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols". In the real symbols condition, the two policies are displayed with three symbolic brand elements, which have been used in EPM's public communications, and became widely recognized by the public. The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second element is the green color, which is strongly associated with taking care of the environment. The third element is an image of a celebrity comedian from an advertising campaign of the EPM. The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman. The recycling policy (in the real symbols condition) was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images. Finally, in the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people. The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic brand elements (i.e. the symbolic effect) from a possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy. The symbols conditions are displayed in **Appendix B**. Further details about the real and fake symbols are found in section ## of the supplementary appendix.

@@

Each policy plan was followed by six questions about respondents' trust in the policy. After the trust questions of the second policy, the subjects were asked additional questions about the two policies, including the degree to which they perceive each of them as personally relevant. These questions were followed by an Instructional Manipulation Check (IMC) item, intended to assess participants’ diligence. The last sections included a set of demographic questions including questions about their place of residence and work, and manipulation checks for participants' familiarity with the real symbols. At the end of the survey, the participants were briefed about the manipulations, and the possible deception.

In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy. I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions. Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.

I further conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the aforementioned interactions. I conducted these estimations after the data collection and analyses, based on the analytical sample size. The estimated detectable (power=0.8) interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs. As for the interactions with the relevance manipulation (among Haifa Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively. The power estimations are reported in details in Section ## of the supplementary appendix.

@@

[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings. Analyses for the information manipulation largely confirm that participants perceived both conditions as reliable.

@@

I begin by examining the random assignment to the different experimental conditions. `r table.x=table.x+1`**Tables `r table.x`** compares between the different conditions, within each of the two areas, on demographic variables and pre-manipulation covariates. These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The table furter suggests that the samples of Haifa Bay and Center residents are fairly balanced with regard to gender, trust in national-level government ministries and interest in environmental issues. Yet, Haifa Bay respondents are somewhat older, more educated, and have more left-wing ideology.

[^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups -- regarding education levels and the percentage of parents; and between the information groups -- regarding the percentage of parents for young children. To adjust for small finite-sample imbalances, as well as for differences between the areas, I also control for covariates in the regression analyses.

@@

I now turn to exploring the main outcome variable of interest -- respondents trust in the *air-pollution policy*. This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), which entails that more subjects reported very low levels of trust, than very high levels of trust in than policy. `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas. The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`]. Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test). The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score. Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a score of 2 or less which indicates very low level of trust, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group. As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`]. Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`). Descriptively, `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than 4, the scale's middle point (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects). This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.

@@

Next, I examine the interactions between the symbols and information manipulation, and the two areas. To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>). Likewise, I expect Haifa Bay respondents to be more affected by the differences in the argument quality of the communication (strong versus weak information), compared with center respondents (H<sub>2</sub>). `r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (displayed in the left panel), the results show that the symbols had a greater positive effect on those living in the polluted Haifa Bay area. Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group. The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups. However, these differences were smaller compared with the effect among the Haifa Bay subjects, and not sufficiently significant. The effects of the information manipulation on the two groups are presented in the right panel. This comparison shows that the differences between participants' trust in the weak and strong policies were roughly similar in both groups.

[^footnote_raw_means]: Means and SDs of outcome variables across the two areas and the experimental conditions are reported in section XX of the supplementary appendix.

@@

These results are at odds with the initial theoretical expectations. They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication (and to a lesser extent, by the unfamiliar graphical elements in the fake symbols). Similarly, these analyses do not provide evidence that Haifa Bay residents were more likely than others to scrutinize the communication, and differentiate between strong and weak arguments.

@@

[^footnote_heteroskedacity]: Breusch-Pagan test confirms the presence of heteroskedasticity (for Model 1.3, Breusch-Pagan test =  `r bptest(mod_air_1.3)[["statistic"]][["BP"]] %>% round(3)`, *p*=`r bptest(mod_air_1.3)[["p.value"]][["BP"]] %>% round(3)`). Robust standard errors are estimated using R sandwich package with estimation type "HC1".

@@

Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content. Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence a concern of endogeneity cannot be entirely ruled. Accordingly, the null findings regarding the interactions between the areas and the manipulations can be resulted by other, unobserved differences between the two populations. Yet, as explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation. I now discuss the results of these two tests.

`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`). Overall, these models reveal relatively similar patterns to those found in the air-pollution policy. Notice that Haifa Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry. The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbols, and the two areas responded similarly to the differences in the information. The fact that similar patterns are observed across the these policies further weakens the hypotheses regarding the moderating role of personal relevance. It also rules out a possible argument that greater relevance enhances (rather then reduces) the effect of symbols. If this was the case, then we should not have found a similar interaction in relation to the recycling policy.

@@

Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations. In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations. Similarly to the regression tables presented above, the final two models are robust analyses where I add controls (Model `r table.x`.3) and restrict the sample to the policy presented first in order (Model `r table.x`.4). In all these models, the coefficient of the relevance treatment is negative but far from significance. The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the incerase in trust due to the appearance of the symbols and those who did not were slightly smaller. However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group) and far from significance. The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]

@@

The limitations of this study should be acknowledged. The study focuses, empirically, on one local policy case. Future studies may put these findings to further test by testing cases of air-pollution policy in other countries, as well as by exploring additional cases of public organizations and policy areas. Additionally, as already acknowledged in the paper, I cannot entirely rule out the possibility that the differences in personal relevance between the two geographic areas are confounded with other differences associated with people's beliefs about the subject. Future studies may put these findings to a more rigorous test through natural experimental or quasi-experimental designs that take advantage of random allocation of citizens to varying levels of personal relevance. Finally, whereas this study includes an experimental manipulation for perceived personal relevance, I acknowledge the limitations of that test, namely its statistical power and the fact that the data does not confirm the its effectiveness in altering the moderating variable. Therefore, future studies may use different, possibly stronger experimental manipulations for testing that variable.
